Inverse Problems --- Example Sheet 1

### 2020-10-28 distribution_theory/C2.tex
I. Hate. Matlab.

>>>>

\section{Tempered distributions and Fourier analysis}
\subsection{Functions of rapid decay}
\begin{definition}
	For any $f \colon \RR^n \to \CC$ and multi-indices $\alpha, \beta$ we define $\norm{f}_{\alpha, \beta} \ceq \sup_{x \in \RR^n} \abs{x^\alpha \pt^\beta\phi}$.

	We define the \emph{Schwarz space}
	\[
	\Cal S(\RR^n) \ceq \qty{f \in C^\infty(\RR^n) : \norm{f}_{\alpha, \beta} < \infty \text{ for all $\alpha, \beta$}}.
	\]

	We say that a sequence $(\phi_n) \subseteq \SS(\RR^n)$ converges to 0 if $\norm{\phi_m}_{\alpha, \beta} \to 0$ for every $\alpha, \beta$.  
\end{definition}

\begin{example}
	The function $x \mapsto \exp(-\norm{x}^2)$ lies in $\SS(\RR^n)$. 
\end{example}

\begin{proposition}
	For all $n$ we have that $\SS(\RR^n) \subseteq L^1(\RR^n)$. 
\end{proposition}

\begin{proof}
	Let $\phi \in \SS(\RR^n)$, then for all $N \in \NN$ we have
	\[
	\int_{\RR^n} \abs{\phi(x)} \dd{x} = \int_{\RR^n} (1 + \norm{x})^{-N} (1 + \norm{x})^N \abs{\phi(x)} \dd{x} \overset?\leq C\sum_{\abs{\alpha} \leq N} \norm{\phi}_{\alpha, 0} \int_{\RR^n} (1 + \norm{x})^{-N} \dd{x}.
	\]

	Since $\int_{\RR^n} (1 + \norm{x})^{-N} \dd{x}$ is finite for $N$ large enough (??), this proves the claim. 
\end{proof}

\begin{definition}
	A linear map $u \colon \SS(\RR^n) \to \CC$ is called a \emph{tempered distribtion} if there exists constants $C, N$ such that
	\[
	\abs{\ang{u, \phi}} \leq C \sum_{\abs{\alpha}, \abs{\beta} \leq N} \norm{\phi}_{\alpha, \beta} \quad\text{for all $\phi \in \SS(\RR^n)$}. 
	\]
\end{definition}
This definition is equivalent to sequential continuity.

\subsection{The Fourier transform on $\SS(\RR^n)$}

\begin{convention}
	We write $D \ceq -i\pt$ and $D^\alpha = (-i)^{\abs{\alpha}} \pt^\alpha$. 
\end{convention}

\begin{definition}
	For $f \in L^1(\RR^n)$, define the \emph{Fourier transform} of $f$ by  
	\[
	[\FF(f)](\lambda) = \hat f(\lambda) \ceq \int_{\RR^n} e^{-i\lambda x} f(x) \dd{x} \quad\text{where $\lambda \in \RR^n$}. 
	\]
\end{definition}

\begin{lemma}
	If $f \in L^1(\RR^n)$, then $\hat f$ is continuous. 
\end{lemma}

\begin{proof}
	If $\lambda_m \to \lambda \in \RR^n$, then by the dominated convergence theorem we have
	\[
	\hat f(\lambda_m) = \int_{\RR^n} e^{-i\lambda_m x} f(x) \dd{x} \overset{\text{DCT}}= \int_{\RR^n} e^{-i\lambda x} f(x) \dd{x} = \hat f(\lambda),
	\]
	where we were able to use the dominated convergence theorem since the integrand is absolutely bounded by $\abs{f}$ and $f \in L^1$. 
\end{proof}

It turns out that this idea generalises: the faster the function $f$ decays, the smoother the Fourier transform $\hat f$ is.

\begin{lemma}
	For $\phi \in \SS(\RR^n)$, we have $\FF[D_x^\alpha \phi](\lambda) = \lambda^\alpha \hat\phi(\lambda)$ and $\FF[x^\beta\phi](\lambda) = (-1)^{\abs{\beta}} D_\lambda^\beta \hat\phi(\lambda)$. 
\end{lemma}

\begin{proof}
	Since $\abs{x^\alpha D^\beta\phi} \to 0$ as $\norm{x} \to \infty$, we have using integration by parts
	\begin{align*}
		\FF[D_\lambda^\alpha\phi](\lambda) &= \int_{\RR^n} e^{-i\lambda x} D_x^\alpha \phi(x) \dd{x} \\
		&= (-1)^{\abs{\alpha}} \int_{\RR^n} D_x^\alpha(e^{-i\lambda x}) \phi(x) \dd{x} \\
		&= \lambda^\alpha\hat\phi(\lambda). 
	\end{align*}

	For the second part of the lemma, by differentiation under the integral sign we get
	\begin{align*}
		 \FF[x^\beta \phi](\lambda) &=  \int_{\RR^n} e^{-i\lambda x} x^\beta \phi(x) \dd{x} \\
		 &= \int_{\RR^n} ((-D_\lambda)^\beta e^{-i\lambda x}) \phi(x) \dd{x} \\
		 &= (-1)^{\abs{\beta}} D_\lambda^\beta \hat\phi(\lambda).
	\end{align*}
\end{proof}

We define the \emph{inverse Fourier transform} by 
\[
\FF^{-1}[\hat f](x)  \ceq \frac{1}{(2\pi)^n} \int_{\RR^n} e^{i\lambda x} \hat f(\lambda) \dd{\lambda}. 
\]
We will now show that on $\SS(\RR^n)$, the inverse Fourier transform is indeed an inverse:
\begin{theorem}
	The Fourier transform $\FF$ defines a continuous isomorphism from $\SS(\RR^n)$ to itself. 
\end{theorem}

\begin{proof}
	Let $\phi \in \SS(\RR^n)$. First, we show that $\hat\phi \in \SS(\RR^n)$: by the previous lemma we have for multi-indices $\alpha, \beta$ that
	\begin{align}
		\abs{\lambda^\alpha (-D_\lambda)^\beta \hat\phi(\lambda)} &= \abs{\lambda^\alpha \FF[x^\beta\phi](\lambda)} = \abs{\FF[D^\alpha_x (x^\beta\phi)](\lambda)} = \abs{\int_{\RR^n} e^{-i\lambda x} D^\alpha(x^\beta\phi) \dd{x}} \nonumber \\
		&\leq \int_{\RR^n} \abs{D^\alpha (x^\beta\phi)} \dd{x} \label{eq:fourier_schwarz_estimate},
	\end{align}
which is finite since $D^\alpha (x^\beta\phi)$ is also a Schwarz function and therefore integrable.

From the previous lemma we also infer that $\hat\phi$ is smooth, so indeed we have $\hat\phi \in \SS(\RR^n)$. 
From \cref{eq:fourier_schwarz_estimate} it is also easily seen that if $\phi_m \to 0$ in $\SS(\RR^n)$, then $\hat\phi_m \to 0$ in $\SS(\RR^n)$ also, which shows that $\FF$ is continuous.

To prove surjectivity and injectivity, we will show that $\FF^{-1}[\FF[f]](x) = f(x)$ (???). Indeed we have
\begin{align*}
	\FF^{-1} [\FF[\phi]](x) &= \frac{1}{(2\pi)^n} \int_{\RR^n} \int_{\RR^n} e^{i\lambda (x-y)} \phi(y) \dd{y}\dd{\lambda} \\
	&= \frac{1}{(2\pi)^n} \lim_{\eps \downarrow 0} \int_{\RR^n} \int_{\RR^n} e^{i \lambda ( x- y) - \eps\norm{\lambda}^2} \phi(y) \dd{y}\dd{\lambda} \\
	&\overset\star= \frac{1}{(2\pi)^n}\lim_{\eps \downarrow 0} \int_{\RR^n} \phi(y)\int_{\RR^n} e^{i\lambda(x- y) - \eps\norm{\lambda}^2} \dd{\lambda} \dd{y},
	%&= \frac{1}{(2\pi)^n} \int_{\RR^n}\int_{\RR^n} e^{i\lambda(x- y)} \dd{\lambda} \dd{y}
\end{align*}
where $\star$ follows from Fubini's theorem.

Now we note that 
\[
\int_{\RR^n} e^{i\lambda(x-y) - \eps\norm{\lambda}^2} \dd{\lambda} = \prod_{i=1}^n \int_{\RR^n} e^{i\lambda_j(x_j - y_j) - \eps\lambda_j^2} \dd{\lambda} \overset{\star\star}= \prod_{i=1}^n \qty(\frac\pi e)^{1/2} e^{- \frac{(x_i - y_i)^2}{4\eps}} = \qty(\frac\pi\eps)^{n/2} e^{- \frac{\norm{x - y}^2}{4\eps}}.
\] 
To explain $\star\star$, \TODO.

and plugging that into the above yields 
\begin{align*}
\FF^{-1}[\FF[\phi]](x) &= \lim_{\eps\downarrow 0} 2^{-n}(\pi \eps)^{-n/2} \int_{\RR^n} \phi(y) e^{-\norm{x-y}^2/(4\eps)} \dd{y} \\
&\overset{\star\star\star}= \pi^{-n/2} \lim_{\eps\downarrow0}\int_{\RR^n} \phi(x - 2\sqrt\eps y') e^{-\norm{y'}^2} \dd{y} \\
&\overset{\text{DCT}}=\pi^{-n/2} \phi(x) \int_{\RR^n} e^{-\norm{y'}^2} \dd{y} = \phi(x),
\end{align*}
where $\star\star\star$ follows from the substitution $x - y = 2\sqrt\eps y'$.

Finally, continuity of $\FF^{-1}$ is easily shown with an argument analogous to that for continuity of $\FF$. 
\end{proof}

### 2020-10-28 distribution_theory/distribution_ES1.tex
I. Hate. Matlab.

\begin{proof}
	Let $f \in \DD(\RR^2)$, then we have
	\begin{align*}
		\ang{\pt_x^2 u - \pt_y^2 u, f} &= \ang{\pt_x^2 u, f}- \ang{\pt_y^2 u, f} = \ang{u, \pt_x^2 f} - \ang{u, \pt_y^2 f} = \ang{u, \pt_x^2 f - \pt_y^2 f} \\
		&\overset\star= \int_{-\infty}^\infty \int_{y}^\infty \pt_x^2 f(x, y) \dd{x}\dd{y} - \int_{-\infty}^\infty \int_{-\infty}^x \pt_y^2 f(x, y) \dd{y} \dd{x} \\
		&= - \int_{-\infty}^\infty \pt_x f(y, y) \dd{y} - \int_{-\infty}^\infty \pt_y f(x, x) \dd{x}
		\\
		&= - \int_{-\infty}^\infty (\pt_xf + \pt_yf)(x, x) \dd{x}.
	\end{align*}
Here, $\star$ follows from Fubini's theorem. 
Define $g(x) = f(x, x)$, then it is easily seen that $g'(x) = \pt_x f(x, x) + \pt_y f(x, x)$, so we find that
\[
\ang{\pt_x^2 u - \pt_y^2 u, f} = 
- \int_{-\infty}^\infty g'(x) \dd{x} = \lim_{x\to -\infty} g(x) - \lim_{x\to\infty} g(x) = 0 - 0 = 0. 
\]
\end{proof}

This shows that $\pt_x u - \pt_y u = 0$, or equivalently, that $u$ satisfies the wave equation. 
\end{document}

>>>>

\begin{proof}
	Let $f \in \DD(\RR^2)$, then we have
	\begin{align*}
		\ang{\pt_x^2 u - \pt_y^2 u, f} &= \ang{\pt_x^2 u, f}- \ang{\pt_y^2 u, f} = \ang{u, \pt_x^2 f} - \ang{u, \pt_y^2 f} = \ang{u, \pt_x^2 f - \pt_y^2 f} \\
		&\overset\star= \int_{-\infty}^\infty \int_{y}^\infty \pt_x^2 f(x, y) \dd{x}\dd{y} - \int_{-\infty}^\infty \int_{-\infty}^x \pt_y^2 f(x, y) \dd{y} \dd{x} \\
		&= - \int_{-\infty}^\infty \pt_x f(y, y) \dd{y} - \int_{-\infty}^\infty \pt_y f(x, x) \dd{x}
		\\
		&= - \int_{-\infty}^\infty (\pt_xf + \pt_yf)(x, x) \dd{x}.
	\end{align*}
Here, $\star$ follows from Fubini's theorem. 
Define $g(x) = f(x, x)$, then it is easily seen that $g'(x) = \pt_x f(x, x) + \pt_y f(x, x)$, so we find that
\[
\ang{\pt_x^2 u - \pt_y^2 u, f} = 
- \int_{-\infty}^\infty g'(x) \dd{x} = \lim_{x\to -\infty} g(x) - \lim_{x\to\infty} g(x) = 0 - 0 = 0. 
\]
This shows that $\pt_x u - \pt_y u = 0$, or equivalently, that $u$ satisfies the wave equation. 
\end{proof}

\begin{question}
	Compute $\Delta(\norm{x}^{2-n})$ in $\DD'(\RR^n)$ for $n \geq 3$, i.e.\ compute
	\[
	\ang{\Delta (\norm{x}^{2-n}), \phi} = \ang{\norm{x}^{2-n}, \Delta\phi} = \int \frac{\Delta\phi}{\norm{x}^{n-2}} \dd{x}
	\]
	for arbitrary $\phi \in \DD(\RR^n)$. Note that $\norm{x} = (x_1^2 +\dotsb +x_n^2)^{1/2}$ and $\Delta = \sum_i (\pdv{x_i})^2$.

	\emph{Hint:} use $\int\dd{x} = \int_{\norm{x}\leq\eps}\dd{x} + \int_{\norm{x}>\eps}\dd{x}$ and treat each integral separately. 
\end{question}

\begin{solution}
	We follow the hint: let $\eps > 0$, then we first compute
	\[
	\int_{\norm{x} > \eps} \frac{\Delta\phi}{\norm{x}^{n-2}} \dd{x} = \sum_{i=1}^n \int_{\norm{x} > \eps} \frac{\pdv[2]{x_i} \phi}{\norm{x}^{n-2}}\dd{x} = \sum_{i=1}^n \int_{\norm{x} > \eps} \phi \cdot \pdv[2]{x_i} \norm{x}^{2-n} \dd{x}. 
	\]
	Now, it is easily computed that $\pdv{x_i} \norm{x} = \frac{x_i}{\norm{x}}$, and therefore 
	\begin{align*}
	\pdv[2]{x_i} \norm{x}^{2-n} &= \pdv{x_i} (2-n) x_i \norm{x}^{-n} = (2-n) \qty(\norm{x}^{-n} - n x_i^2 \norm{x}^{-n-2}) \\
	&= (n-2)\norm{x}^{-n} \qty(n \qty(\frac{x_i}{\norm{x}})^2 - 1). 
	\end{align*}
\end{solution}

\end{document}

### 2020-10-28 inverse_problems/inverse_ES1.tex
I. Hate. Matlab.

\item We know that the adjoint is the unique operator that satisfies $\ang{Au, v} = \ang{u, A^*v}$ for all $u, v \in \XX$. Let $u, v \in \XX$, then we compute
\begin{align*}
	\ang{Au, v} &= \int_\Omega (Au)(y)\cdot  v(y) \dd{y} = \int_\Omega \qty(\int_\Omega k(x, y) u(x) \dd{x}) v(y) \dd{y} \\
	&= \int_\Omega\int_\Omega k(x, y) u(x) v(y) \dd{x} \dd{y} \overset\star= \int_\Omega\int_\Omega k(x, y) u(x) v(y) \dd{y} \dd{x} \\
	&= \int_\Omega u(x) \qty(\int_\Omega k(x, y) v(y) \dd{y}) \dd{x} = \ang{u, A^*v}
\end{align*}
where $(A^* v)(x) = \int_\Omega k(x, y) v(y) \dd{y}$ as required. Here $\star$ follows from Fubini's theorem (\TODO justify).

\item It is known that for any compact set $X \subseteq \RR^n$, polynomials lie dense in $L^2(X)$. Therefore, there exists a sequence of polynomials $p_n$ such that $p_n \to k$ in $L^2([0, 1]^4)$. It is easily seen that for any polynomial $p$, the operator
\[
(A_p u)(y) \ceq \int_\Omega p(x, y) u(x) \dd{x} 
\] 
has finite rank: let $p(z) = \sum_{\abs{\alpha} \leq n} c_\alpha z^\alpha$ (where $z \in [0, 1]^4$ and $\alpha$ is a multi-index), then we find
\[
(A_p u)(y) = \sum_{\abs{\alpha} \leq n} c_\alpha \int_\Omega x_1^{\alpha_1} x_2^{\alpha_2} y_1^{\alpha_3} y_2^{\alpha_4} u(x) \dd{x} = \sum_{\abs{\alpha} \leq n} c_\alpha \qty(\int_\Omega x_1^{\alpha_1} x_2^{\alpha_2} \dd{x}) y_1^{\alpha_3} y_2^{\alpha_4},
\]
so $A_p u$ lies in the $\Span\qty{y_1^{\alpha_1} y_2^{\alpha_2} \mid \alpha_1 + \alpha_2 \leq n}$, and therefore has finite rank. 
By (b), we find that $\norm{A - A_n} \leq \norm{k - p_n} \to 0$, which shows that $A_n \to A$ in operator norm. We conclude that $A$ is compact. 
%\[
%(A_n u)(y) \ceq \int_\Omega p_n()
%\]
	\end{enumerate}
\end{solution}

@@

	% \item From Fourier theory it is known that $\qty{s_n(x) = \sqrt 2\sin(nx) : n \in \NN}$ and $\qty{1} \cup \qty{c_n(x) = \sqrt 2\cos(nx) \mid n \in \NN}$ are orthonormal bases of $L^2[0, 1]$. 
	%Note that 
	%\[
	%(A s_n)(y) = \int_0^y s_n(x) \dd{x} = \sqrt 2 \int_0^y \sin(nx) \dd{x} = \frac{\sqrt 2}{n} \qty(1 - \cos(ny)) = \frac{\sqrt 2}{n} c_0(y) - \frac1n c_n(y) 
	%\]
	\item 	Note that $A$ is compact, since we can write $(Au)(y) = \int_{[0, 1]} k(x, y) u(x) \dd{x}$ with $k(x, y) = \ind_{x \leq y}$.

	To apply the Picard criterion we must find the singular values and right singular vectors of $A$, which are equal to the square roots of the eigenvalues of $AA^*$ and the eigenvectors of $AA^*$.

	\begin{align*}
		\ang{Au, v} &= \int_0^1 (Au)(y)\cdot v(y) \dd{y} \\
		&= \int_0^1 \int_0^y u(x) \dd{x} v(y) \dd{y} \\
		&= \int_0^1 \int_0^y u(x) v(y) \dd{x} \dd{y} \\
		&= \int_0^1 \int_x^1 u(x) v(y) \dd{y} \dd{x} \\ 
		&= \int_0^1 u(x) \int_x^1 v(y) \dd{y} \dd{x} \\
		&= \ang{u, A^* v}
	\end{align*}
where $v(x) = \int_x^1 v(y) \dd{y}$.  Therefore, we find
\begin{align*}
	(AA^* u)(x) = \int_0^x \int_y^1 u(z) \dd{z} \dd{y}.
\end{align*}
Now we solve the eigenequation. Firstly, note that $\Nul(A) = \qty{0}$, so let $\lambda^2 > 0$. Then we have
\begin{align}
	\int_0^x \int_y^1 u(z) \dd{z} \dd{y} &= \lambda^2 u(x) \\
	\int_x^1 u(z) \dd{z} &= \lambda^2 u'(x) \\
	- u(x) &= \lambda^2 u''(x). 
\end{align}
Furthermore, from (1) we infer $u(0) = 0$ while from (2) we infer $u'(1) = 0$. 
The general solution to (3) is given by $u(x) = a \cos(\lambda^{-1} x) + b \sin(\lambda^{-1} x)$. 
Plugging $u(0) = 0$ gives $a = 0$, and $u'(1) = 0$ gives
\[
b\lambda^{-1} \cos(\lambda^{-1}) = 0 \implies b = 0 \text{ or } \lambda^{-1} = \pi\qty(n - \frac12) \text{ for some $n \in \ZZ_{>0}$}.
\]

Our singular values are therefore $\frac{1}{(n - \frac12)\pi}$ ($n \in \ZZ_{>0}$) with right singular vectors $y_n(x) = \sqrt 2\sin((n - \frac12) \pi x)$. 
We now compute
\[
\ang{f, y_n} = \sqrt 2\int_{1/2}^1 \sin(\qty(n - \frac12) \pi x) \dd{x} = ...
\]

\item The Moore-Penrose inverse of $A$ is discontinuous. This can be seen by theorem 2.1.11: in (a) we have constructed a sequence $(f_n) \subseteq \Ran(A)$ that converges, and in (b) we have shown that its limit lies outside of $\Ran(A)$. Therefore, $\Ran(A)$ is not closed, so $A\D$ is discontinuous.

@@

			\item If $A\T A = I$, then the columns $\vec u_1, \dotsc, \vec u_n$ of $A$ are orthogonal. In particular, $A$ is injective (so $\Nul(A) = \qty{0}$) and $\Ran(A) = \Span\qty{\vec u_1, \dotsc, \vec u_n}$. Extend $\vec u_1, \dotsc, \vec u_n$ to an orthonormal basis $\vec u_1, \dotsc, \vec u_m$ of $\RR^m$, then we must have
			\[
			A\D\qty(\sum_{i=1}^m \alpha_i \vec u_i) = \mqty(\alpha_1 \\ \vdots \\ \alpha_n) \in \RR^n.
			\]
			From this expression it is easily seen that $A\D = A\T$. 
		\end{enumerate}

>>>>

\item We know that the adjoint is the unique operator that satisfies $\ang{Au, v} = \ang{u, A^*v}$ for all $u, v \in \XX$. Let $u, v \in \XX$, then we compute
\begin{align*}
	\ang{Au, v} &= \int_\Omega (Au)(y)\cdot  v(y) \dd{y} = \int_\Omega \qty(\int_\Omega k(x, y) u(x) \dd{x}) v(y) \dd{y} \\
	&= \int_\Omega\int_\Omega k(x, y) u(x) v(y) \dd{x} \dd{y} \overset\star= \int_\Omega\int_\Omega k(x, y) u(x) v(y) \dd{y} \dd{x} \\
	&= \int_\Omega u(x) \qty(\int_\Omega k(x, y) v(y) \dd{y}) \dd{x} = \ang{u, A^*v}
\end{align*}
where $(A^* v)(x) = \int_\Omega k(x, y) v(y) \dd{y}$ as required. Here $\star$ follows from Fubini's theorem.

\item It is known that for any compact set $X \subseteq \RR^n$, polynomials lie dense in $L^2(X)$. Therefore, there exists a sequence of polynomials $p_n$ such that $p_n \to k$ in $L^2([0, 1]^4)$. It is easily seen that for any polynomial $p$, the operator
\[
(A_p u)(y) \ceq \int_\Omega p(x, y) u(x) \dd{x} 
\] 
has finite rank: let $p(z) = \sum_{\abs{\alpha} \leq n} c_\alpha z^\alpha$ (where $z \in [0, 1]^4$ and $\alpha$ is a multi-index), then we find
\[
(A_p u)(y) = \sum_{\abs{\alpha} \leq n} c_\alpha \int_\Omega x_1^{\alpha_1} x_2^{\alpha_2} y_1^{\alpha_3} y_2^{\alpha_4} u(x) \dd{x} = \sum_{\abs{\alpha} \leq n} c_\alpha \qty(\int_\Omega x_1^{\alpha_1} x_2^{\alpha_2} u(x) \dd{x}) y_1^{\alpha_3} y_2^{\alpha_4},
\]
so $A_p u$ lies in the $\Span\qty{y_1^{\alpha_1} y_2^{\alpha_2} \mid \alpha_1 + \alpha_2 \leq n}$, and therefore has finite rank. 
By (b), we find that $\norm{A - A_n} \leq \norm{k - p_n} \to 0$, which shows that $A_n \to A$ in operator norm. We conclude that $A$ is compact. 
%\[
%(A_n u)(y) \ceq \int_\Omega p_n()
%\]
	\end{enumerate}
\end{solution}

@@

	\item 	In example 2.2.12, it is shown that for this operator, the Picard criterion is
	\begin{equation} \label{eq:picard}
	2\sum_{j=1}^\infty  \sigma_j^{-2} \qty(\int_0^1 f(s) \sin(\sigma_j^{-1} s) \dd{s})^2,
	\end{equation}
	where $\sigma_j = \frac2{(2j - 1)\pi}$.

	We compute
	\[
	\int_0^1 f(s) \sin(\sigma_j^{-1} s) \dd{s} = \int_{1/2}^1 \sin(\sigma_j^{-1} s) \dd{s} = \sigma_j \qty[ \cos(\frac12 \sigma_j^{-1}) - \cos(\sigma_j^{-1})]. 
	\]
	We have
	\[
	\cos(\sigma_j^{-1}) = \cos(\frac{(2j - 1)\pi}{2}) = 0 \quad\text{and}\quad \cos(\frac12\sigma_j^{-1}) = \cos(\frac{(2j-1)\pi}{4}) = \pm\frac1{\sqrt2 }. 
	\]

	Plugging this into \cref{eq:picard} gives that
	\[
	2\sum_{j=1}^\infty  \sigma_j^{-2} \qty(\int_0^1 f(s) \sin(\sigma_j^{-1} s) \dd{s})^2 = 2 \sum_{j=1}^\infty \sigma_j^{-2} (\sigma_j^2/2) = \sum_{j=1}^\infty 1 = \infty,
	\]
	so $f$ does not satisfy the Picard criterion and therefore $f \in \clos{\Ran(A)} \setminus \Ran(A)$. 
%	Note that $A$ is compact, since we can write $(Au)(y) = \int_{[0, 1]} k(x, y) u(x) \dd{x}$ with $k(x, y) = \ind_{x \leq y}$. 
%	
%	To apply the Picard criterion we must find the singular values and right singular vectors of $A$, which are equal to the square roots of the eigenvalues of $AA^*$ and the eigenvectors of $AA^*$. 
%	
%
%	\begin{align*}
%		\ang{Au, v} &= \int_0^1 (Au)(y)\cdot v(y) \dd{y} \\
%		&= \int_0^1 \int_0^y u(x) \dd{x} v(y) \dd{y} \\
%		&= \int_0^1 \int_0^y u(x) v(y) \dd{x} \dd{y} \\
%		&= \int_0^1 \int_x^1 u(x) v(y) \dd{y} \dd{x} \\ 
%		&= \int_0^1 u(x) \int_x^1 v(y) \dd{y} \dd{x} \\
%		&= \ang{u, A^* v}
%	\end{align*}
%where $v(x) = \int_x^1 v(y) \dd{y}$.  Therefore, we find
%\begin{align*}
%	(AA^* u)(x) = \int_0^x \int_y^1 u(z) \dd{z} \dd{y}.
%\end{align*}
%Now we solve the eigenequation. Firstly, note that $\Nul(A) = \qty{0}$, so let $\lambda^2 > 0$. Then we have
%\begin{align}
%	\int_0^x \int_y^1 u(z) \dd{z} \dd{y} &= \lambda^2 u(x) \\
%	\int_x^1 u(z) \dd{z} &= \lambda^2 u'(x) \\
%	- u(x) &= \lambda^2 u''(x). 
%\end{align}
%Furthermore, from (1) we infer $u(0) = 0$ while from (2) we infer $u'(1) = 0$. 
%The general solution to (3) is given by $u(x) = a \cos(\lambda^{-1} x) + b \sin(\lambda^{-1} x)$. 
%Plugging $u(0) = 0$ gives $a = 0$, and $u'(1) = 0$ gives
%\[
%b\lambda^{-1} \cos(\lambda^{-1}) = 0 \implies b = 0 \text{ or } \lambda^{-1} = \pi\qty(n - \frac12) \text{ for some $n \in \ZZ_{>0}$}.
%\]
%
%Our singular values are therefore $\frac{1}{(n - \frac12)\pi}$ ($n \in \ZZ_{>0}$) with right singular vectors $y_n(x) = \sqrt 2\sin((n - \frac12) \pi x)$. 
%We now compute
%\[
%\ang{f, y_n} = \sqrt 2\int_{1/2}^1 \sin(\qty(n - \frac12) \pi x) \dd{x} = ...
%\]

\item The Moore-Penrose inverse of $A$ is discontinuous. This can be seen by theorem 2.1.11: we have in (b) an element $f \in \clos{\Ran(A)} \setminus \Ran(A)$, so   $\Ran(A)$ is not closed, so $A\D$ is discontinuous.

@@

			\item 
%			If $A\T A = I$, then the columns $\vec u_1, \dotsc, \vec u_n$ of $A$ are orthogonal. In particular, $A$ is injective (so $\Nul(A) = \qty{0}$) and $\Ran(A) = \Span\qty{\vec u_1, \dotsc, \vec u_n}$. Extend $\vec u_1, \dotsc, \vec u_n$ to an orthonormal basis $\vec u_1, \dotsc, \vec u_m$ of $\RR^m$, then we must have
%			\[
%			A\D\qty(\sum_{i=1}^m \alpha_i \vec u_i) = \mqty(\alpha_1 \\ \vdots \\ \alpha_n) \in \RR^n.
%			\]
%			From this expression it is easily seen that $A\D = A\T$.
			We claim $A\D = A\T$. For this, we check the first two Moore-Penrose equations: for the first one, we have $A\T A = I_n = P_{\RR^n} = P_{\Nul(A)\P}$ since $\Nul(A) = \qty{0}$.  
			For the second one, let $\vec u_1, \dotsc, \vec u_n \in \RR^m$ be the columns of $A$ (which are orthonormal), then we have
			\[
			AA\T = \sum_{i=1}^n \vec u_i \vec u_i\T = P_{\Span\qty{\vec u_1, \dotsc, \vec u_n}} = P_{\clos{\Ran(A)}}. 
			\]
		\end{enumerate}
